Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
nouns to verbs

Building on the massively parallelizable \gls{MOOSE} framework allows Moltres
to be run on super-computing platforms like \gls{NCSA}'s Blue Waters. For some
three-dimensional simulations, the number of
elements in the mesh and total number of degrees of freedom exceed one million
and ten million respectively. To handle problems of this size, Moltres has been
run on up to 608 cores. However, reducing the problem dimension from three to
two and using a structured mesh that can be much more coarse in the axial
direction allows problem solution to be carried out on a single core in under
five minutes.

>>>>

Building on the massively parallelizable \gls{MOOSE} framework allows Moltres
to be run on super-computing platforms like \gls{NCSA}'s Blue Waters. For some
three-dimensional simulations, the number of
elements in the mesh and total number of degrees of freedom exceed one million
and ten million respectively. To handle problems of this size, Moltres has been
run on up to 608 cores. However, reducing the problem dimension from three to
two and using a structured mesh that can be much more coarse in the axial
direction allows the problem to be solved on a single core in under
five minutes.
